DeepPicar:​ ​A​ ​Low-cost​ ​Deep​ ​Neural​ ​Network-based​ ​Autonomous​ ​Car

### 2017-10-01 paper/background.tex
revision

In this section, we provide background on the application of deep
learning in robotics, particulary autonomous vehicles.

@@

To solve the problem of autonomous driving, a standard approach has
been decomposing the problem into multiple sub-problems,
such as lane marking detection, path planning, and low-level
control, which together form a processing pipeline~\cite{Bojarski2016}.
Recently, researchers are exploring another approach that dramatically
simplifies the standard control pipeline by applying deep neural
networks to directly produce control outputs from senor
inputs~\cite{Levine2016}. Figure~\ref{fig:end-to-end-control}
shows the differences between two two approaches.

@@

Recent successes in AI, including the NVIDIA's DAVE-2 showing, are due
in large part to the increased computing capability of computers,
which affored researchers to train ever deeper networks with high
accuracy. In automotive systems,

- computing has been a obstacle.
- performance, but also constraints size, weight, and power as well as
cost senstive nature of industries including automtive.
- many new embeded computing platforms emerged: affordable and
powerful. raspberry pi, nvidia's embedded platforms tout their
superiority in GPU based acceleration of the AI tasks.

Our primary objective of this study are
- to understand the necessary computing performance for applying AI
technology based robotics systems, and 
- what kind of computing architecture and runtime supports
are most appropriate for such workload.

Toward to achieve the two goals, we implement a low-cost autonomous
car platform as a case study, as we will explain in the following
section.

>>>>

In this section, we provide background on the application of deep
learning in robotics, particularly autonomous vehicles.

@@

To solve the problem of autonomous driving, a standard approach has
been decomposing the problem into multiple sub-problems,
such as lane marking detection, path planning, and low-level
control, which together form a processing pipeline~\cite{Bojarski2016}.
Recently, researchers are exploring another approach that dramatically
simplifies the standard control pipeline by applying deep neural
networks to directly produce control outputs from senor
inputs~\cite{Levine2016}. Figure~\ref{fig:end-to-end-control}
shows the differences between two approaches.

@@

Recent successes in AI, including NVIDIA's DAVE-2 showing, are due
in large part to the increased computing performance,
which afforded researchers to train and use ever deeper neural networks with
high accuracy. For practical, a computer platform in an automotive vehicle must
satisfy two often conflicting goals. One the one hand, the platform must provide
enough computing capacity for real-time processing of computationally expensive
AI workloads. On the other hand, the platform must also satisfy various
constrains such as cost, size, weight, and power consumption limits.
Because of these reasons, finding a right computing platform is non-trivial
task, one that requires deep understanding of the workloads and their
characteristics as well as the hardware platform that executes the
workloads. It is further complicated by the heterogeneity of available
computing hardware resources---multicore, GPU, DSP and other specialized
hardware accelerators.

The primary objective of this study are (1) to understand the necessary
computing performance for applying AI technology based robotics systems, and
(2) what kind of computing architecture and runtime supports
are most appropriate for such workload.
Toward to achieve the two goals, we implement a low-cost autonomous
car platform as a case study, as we will explain in the following
section.
